Single Site, Single Disturbance

### 2021-02-02 SingleSite_SingleDisturb.Rmd
update SSSD to lower disturbance rate, larger ensemble, and saving of key results to a RData file that's read by the paper code (knits into paper itself)

```{r,echo=1:2, fig.width=7, fig.height=6}
set.seed(1066)
p.dist = 0.05
n0 = 1
nIC = 6
r = .1
K = 6
n.sd = 0.25
NT = 100
time = 1:NT
xlim = c(5,25)
n = rep(nIC,NT)
d = rep(0,NT)
d[10] = 1  ## prescribe a disturbance
for(t in 2:NT){
  n[t] = n[t-1] + r*n[t-1]*(1-n[t-1]/K) + rnorm(1,0,n.sd)
#  d[t] = rbinom(1,1,p.dist)
  if(d[t]) n[t] = abs(rnorm(1,n0,0.5))
}

plot(time,n,type='l',ylim=range(n),xlim=xlim,ylab="LAI",lwd=3)
obs.sd = 0.75
n.true=n
n.obs = rnorm(NT,n.true,obs.sd)
points(time,n.obs,pch=18,col=2,cex=1.5)
legend("topleft",legend=c("truth","obs"),lwd=c(2,NA),pch=c(NA,18),col=1:2)
## Simulate less frequent observations
#na.seq = 1:NT; na.seq=na.seq[-seq(1,NT,by=5)]
#n.fia = n.obs;n.fia[na.seq] <- NA
#points(time,n.fia,pch=18,col="blue",cex=2)
```

@@

```{r}
n0.sd = n.sd
NE = 1000
n0s = rlnorm(NE,log(nIC),n0.sd)
ne0 = matrix(n0s,NE,NT)
for(i in 1:NE){
  for(t in 2:NT){
    ne0[i,t] = abs(ne0[i,t-1] + r*ne0[i,t-1]*(1-ne0[i,t-1]/K) + rnorm(1,0,n.sd))
#    if(rbinom(1,1,p.dist)) ne[i,t] = abs(rnorm(1,n0,0.5))
  }
}
yrng = c(0,8) #range(ne0)
n0.stats = apply(ne0,2,quantile,c(0.025,0.5,0.975))
plot(time,n.obs,type='n',ylim=yrng,xlim=xlim)
polygon(cbind(c(time, rev(time), 1), c(n0.stats[1, ], rev(n0.stats[3, ]),
  n0.stats[1, 1])), border = NA, col = 'lightblue')
lines(time,n0.stats[2,],lwd=2,col="blue4")
points(time,n.obs,pch=18,col=2,cex=1.5)
```

@@

```{r}
n0.sd = n.sd
NE = 1000
n0s = rlnorm(NE,log(nIC),n0.sd)
ne = matrix(n0s,NE,NT)
for(i in 1:NE){
  for(t in 2:NT){
    ne[i,t] = abs(ne[i,t-1] + r*ne[i,t-1]*(1-ne[i,t-1]/K) + rnorm(1,0,n.sd))
    if(rbinom(1,1,p.dist)) ne[i,t] = abs(rnorm(1,n0,0.5))
  }
}
yrng = range(ne)
n.stats = apply(ne,2,quantile,c(0.025,0.5,0.975))
plot(time,n.obs,type='n',xlim=xlim)
polygon(cbind(c(time, rev(time), 1), c(n.stats[1, ], rev(n.stats[3, ]),
  n.stats[1, 1])), border = NA, col = 'lightblue')
lines(time,n.stats[2,],lwd=2,col="blue4")
points(time,n.obs,pch=18,col=2,cex=1.5)
```

@@

```{r}
AnalysisSSSD <- "
model{
  ## prior
  muN ~ dnorm(mufN,pfN)
  muD ~ dnorm(mufD,pfD)
  D ~ dbern(p)
  ## Analysis
  n <- D*muD + (1-D)*muN
  Y ~ dnorm(n,r)
}"
## Storage
CI.fN = matrix(NA,5,NT)
CI.fD = matrix(NA,5,NT)
Dbar = 0
Analysis <- Forecast <- list()
## set IC
nMC = 5000
Xl = nIC         
pl = 1/n.sd^2
Na = rnorm(nMC,Xl,n.sd)
Nf = N*NA

@@

>>>>

```{r,echo=1:2}
#fig.width=7, fig.height=6
set.seed(1066)
p.dist = 0.005
n0 = 1
nIC = 6
r = .1
K = 6
n.sd = 0.25
NT = 100
time = 1:NT
xlim = c(5,25)
n = rep(nIC,NT)
d = rep(0,NT)
d[10] = 1  ## prescribe a disturbance
for(t in 2:NT){
  n[t] = n[t-1] + r*n[t-1]*(1-n[t-1]/K) + rnorm(1,0,n.sd)
#  d[t] = rbinom(1,1,p.dist)
  if(d[t]) n[t] = abs(rnorm(1,n0,0.5))
}

plot(time,n,type='l',ylim=range(n),xlim=xlim,ylab="LAI",lwd=3)
obs.sd = 0.75
n.true=n
n.obs = rnorm(NT,n.true,obs.sd)
points(time,n.obs,pch=18,col=2,cex=1.5)
legend("topright",legend=c("truth","obs"),lwd=c(2,NA),pch=c(NA,18),col=1:2)
## Simulate less frequent observations
#na.seq = 1:NT; na.seq=na.seq[-seq(1,NT,by=5)]
#n.fia = n.obs;n.fia[na.seq] <- NA
#points(time,n.fia,pch=18,col="blue",cex=2)
```

@@

```{r}
n0.sd = n.sd
NE = 10000
n0s = rlnorm(NE,log(nIC),n0.sd)
ne0 = matrix(n0s,NE,NT)
for(i in 1:NE){
  for(t in 2:NT){
    ne0[i,t] = abs(ne0[i,t-1] + r*ne0[i,t-1]*(1-ne0[i,t-1]/K) + rnorm(1,0,n.sd))
#    if(rbinom(1,1,p.dist)) ne[i,t] = abs(rnorm(1,n0,0.5))
  }
}
yrng = c(0,8) #range(ne0)
n0.stats = apply(ne0,2,quantile,c(0.025,0.5,0.975))
plot(time,n.obs,type='n',ylim=yrng,xlim=xlim)
polygon(cbind(c(time, rev(time), 1), c(n0.stats[1, ], rev(n0.stats[3, ]),
  n0.stats[1, 1])), border = NA, col = 'lightblue')
lines(time,n0.stats[2,],lwd=2,col="blue4")
points(time,n.obs,pch=18,col=2,cex=1.5)
```

@@

```{r}
n0.sd = n.sd
NE = 10000
n0s = rlnorm(NE,log(nIC),n0.sd)
ne = matrix(n0s,NE,NT)
for(i in 1:NE){
  for(t in 2:NT){
    ne[i,t] = abs(ne[i,t-1] + r*ne[i,t-1]*(1-ne[i,t-1]/K) + rnorm(1,0,n.sd))
    if(rbinom(1,1,p.dist)) ne[i,t] = abs(rnorm(1,n0,0.5))
  }
}
yrng = range(ne)
n.stats = apply(ne,2,quantile,c(0.025,0.5,0.975))
plot(time,n.obs,type='n',xlim=xlim)
polygon(cbind(c(time, rev(time), 1), c(n.stats[1, ], rev(n.stats[3, ]),
  n.stats[1, 1])), border = NA, col = 'lightblue')
lines(time,n.stats[2,],lwd=2,col="blue4")
points(time,n.obs,pch=18,col=2,cex=1.5)
```

@@

```{r}
AnalysisSSSD <- "
model{
  ## prior
  muN ~ dnorm(mufN,pfN)
  muD ~ dnorm(mufD,pfD)
  D ~ dbern(p)
  ## Analysis
  n <- D*muD + (1-D)*muN
  Y ~ dnorm(n,r)
}"
## Storage
CI.fN = matrix(NA,5,NT)
CI.fD = matrix(NA,5,NT)
Dbar = 0
Analysis <- Forecast <- list()
## set IC
nMC = 5000
Xl = nIC         
pl = 1/n.sd^2
Na = rnorm(nMC,Xl,n.sd)
Nf = Na*NA

@@

lines(an0.stats[3,],col="orange",lwd=2)
lines(an.stats[3,],col="#b2df8a",lwd=2)
#lines(CI.fSSSD[2,],col="blue",lwd=2)
lines(CI.fN[3,],col="blue",lwd=2)
lines(Dbar,lwd=2)
points(data$Y,pch=18,col=2)
legend("topright",legend=c("EnKF, no disturb","EnKF, disturb","Multinomial","data","P(dist)"),
       lwd=5,col=c("orange","#b2df8a","blue","red","black"))

### Save outputs required to include figure in Results
save(data,CI.fN,time,an0.stats,an.stats,NT,Dbar,file="SSSD.RData")
